# main module & framework for bootstrap & crossval

## get all the data
Note: the data has been amended so that class labels M = 1, and B = 0.
```{r} 
data = read.csv("complete_dataset.csv")
trash = data[,1]
X = data[3:length(data)]
y = data[,2]
```

## split into test and train 
```{r} 
p = 0.85
keep = runif(length(length(data[,1]))) < p
X_train = X[keep,]
X_test = X[!keep,]
y_train = y[keep]
y_test = y[!keep]
```

## bootstrapping framework
```{r}

bootstrap_framework = function(X_train, y_train) {
  # constants
  p = 0.85
  iterations = 1000
  models = 10
  results = matrix(0, models, iterations)
  k_fold = 5
  train_length = length(X_train[,1])
  fold_size = as.integer(train_length / k_fold)
  
  for(i in 1:iterations) {
    # generate bootstrapped sample
    bootstrap_ind = sample(train_length,train_length,replace=TRUE)
    X_boot = X_train[bootstrap_ind,]
    y_boot = y_train[bootstrap_ind]
    
    # TODO:
    # store whatever values we need here
    # both for *saving* results, but also different *values of params*
    
    for(k in 1:k_fold) {
      ## split data into train (X_tr, y_tr) and validation (X_val, y_val)
      test_i = ((k - 1) * fold_size): ((k) * fold_size)
      keep = (1:length(X_boot[,1])) * 0 + 1
      keep[test_i] = 0
    
      X_tr = X_boot[keep,]
      y_tr = y_boot[keep]
      
      X_val =  X_boot[!keep,]
      y_val =  y_boot[!keep]
      
      ## TODO: add models to test below
      
      
      
      ## TODO: store results into result matrix
      
    }
  }
  
  
  ## TODO: generate charts, save results, return results or print results
  
  ## TODO: determine best model
  
}
```

## run bootstrap_framework on unpreprocessed data

```{r}
bootstrap_framework(X_train, y_train)
```

## run bootstrap_framework on lasso predictors

```{r}
bootstrap_framework(X_train, y_train)
```

## run bootstrap_framework on pca (variance = 90)

```{r}
bootstrap_framework(X_train, y_train)
```

## run bootstrap_framework on pca (variance = 95)

```{r}
bootstrap_framework(X_train, y_train)
```

## run bootstrap_framework on pca (variance = 99)

```{r}
bootstrap_framework(X_train, y_train)
```

## extra
## figure out semi-supervised learning
